Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-02 draft/accordionComplexSurfaces.tex
minor modif

Case 4: If $\alpha$ stays inside a blue cell, then it rolls around a $\dissection\dual$ puncture. There is a $\dissection\dual$-arc $\beta$ ending in that puncture. When $\alpha$ crosses $\beta$, the puncture stays on the same side of $\alpha$, hence $\alpha$ is not a $\dissection\dual$-slalom.
\end{proof}

@@

\begin{lemma}
\label{lem:walks=arcs}
Walks of $\bar Q$ are precisely arcs between blossom points.
\end{lemma}

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Non-kissing walks = non-crossing $\dissection$-accordion curves = non-crossing $\dissection\dual$-slalom curves.
\end{lemma}

>>>>

Case 4: If~$\alpha$ stays inside a blue cell, then it rolls around a~$\dissection\dual$ puncture.
There is a~$\dissection\dual$-arc~$\beta$ ending in that puncture. When~$\alpha$ crosses~$\beta$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
\end{proof}

@@

\begin{lemma}
\label{lem:walks=arcs}
Walks of~$\bar Q$ are precisely~$\dissection$ accordions.
\end{lemma}

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Non-kissing walks = non-crossing $\dissection$-accordion curves.
\end{lemma}
